### 2012-02-06 docs/getting_started/getting_started.tex
more syncing

Different problems in \maestro\ are contained in individual
sub-directories under {\tt MAESTRO/}.  The {\tt GNUmakefile}
in each problem directory lists the components of {\tt MAESTRO}
that are used to build the executable.

>>>>

Different problems in \maestro\ are contained in one of three
sub-directories under {\tt MAESTRO/} ({\tt SCIENCE/}, {\tt
TEST\_PROBLEMS}, or {\tt UNIT\_TESTS}).  The {\tt GNUmakefile} in each
problem directory lists the components of {\tt MAESTRO} that are used
to build the executable.  {\tt TEST\_PROBLEMS/} contains simple
problems that were used in the development of \maestro.  Many
of these were featured in the papers describing the \maestro\ algorithm.
